### 2024-10-04 manuscript/ms.tex
Working on adding results to manuscript.

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/independent-div-time-scatter.pdf}
        \caption{
            \Ecoevolity estimates divergence times more accurately and precisely
            than \dppmsbayes when all five population pairs diverge independently.
        }
        \label{fig:divtimeindependent}
    \end{center}
\end{figure}

>>>>

\subsection{Simulation results}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-model-distance-cropped.pdf}
        \caption{
            \Ecoevolity estimates the partitioning of population pairs to
            divergence times (the divergence model) more accurately and
            precisely than \dppmsbayes across all simulated numbers of loci
            (columns) and whether the divergence model was drawn from a
            Dirichlet process (top row), or constrained so that all pairs of
            populations diverged independently (middle row) or simultaneously
            (bottom row).
            Divergence model estimation error was quantified for each
            simulation replicate using the mean partition distance
            \citep{Regnier1983,Gusfield2002} between the true divergence model
            and the posterior samples of divergence models.
            Partition distances was calculated using the Hungarian (or
            Kuhn-Munkres) algorithm
            \citep{Kuhn1955,Munkres1957}
            as implemented in \pycoevolity
            \citep[Version 0.2.11 Commit 85ea44b;][]{Oaks2018ecoevolity,PycoevolityRepoOnline},
            which relies on the Munkres Python package
            \citep[Version 1.1.4;][]{Clapper2020}.
            For each violin plot, the sample size (number of simulation
            replicates) is shown beneath and the mean is represented by the
            white dot and shown above.
            The box shows the upper and lower quartiles and the brackets
            show the 2.5th and 97.5th percentiles.
            At the top center of each plot, the results of a Mann-Whitney U
            test \citep{MannWhitney1947} are shown comparing mean model errors
            between \ecoevolity and \dppmsbayes;
            the probability of superiority \citep[PoS, the probability that
            \ecoevolity has a lower mean model error than \dppmsbayes for a
            random simulation replicate drawn from
            each;][]{WolfeHogg1971,Grissom1994} and p-value is provided.
        }
        \label{fig:modelerror}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-div-time-error-cropped.pdf}
        \caption{
            \Ecoevolity better estimates divergence times than \dppmsbayes
            across all simulated numbers of loci (columns) and whether the
            divergence model was drawn from a Dirichlet process (top row), or
            constrained so that all pairs of populations diverged independently
            (middle row) or simultaneously (bottom row).
            Divergence time error was quantified for each simulation replicate
            as the sum of the difference between the true and posterior mean
            divergence time across the five pairs of populations.
            For each violin plot, the sample size (number of simulation
            replicates) is shown beneath and the mean is represented by the
            white dot and shown above.
            The box shows the upper and lower quartiles and the brackets
            show the 2.5th and 97.5th percentiles.
            At the top center of each plot, the results of a Mann-Whitney U
            test \citep{MannWhitney1947} are shown comparing mean model errors
            between \ecoevolity and \dppmsbayes;
            the probability of superiority \citep[PoS, the probability that
            \ecoevolity has a lower mean model error than \dppmsbayes for a
            random simulation replicate drawn from
            each;][]{WolfeHogg1971,Grissom1994} and p-value is provided.
        }
        \label{fig:divtimeerror}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/plots/free-div-time-scatter-cropped.pdf}
        \caption{
            \Ecoevolity (top row) estimates divergence times more accurately
            and precisely than \dppmsbayes (bottom row) across all simulated
            numbers of loci (columns) for five pairs of populations simulated
            to have diverged according to a Dirichlet process.
            Each plotted circle and associated error bars represent the posterior mean
            and 95\% credible interval.
            \accuracyscatterplotannotations{\comparisonetime{}}
        }
        \label{fig:divtimeerrordp}
    \end{center}
\end{figure}

\subsection{Empirical results}

### 2024-10-04 utils/macros.tex
Working on adding results to manuscript.

>>>>

\newcommand{\accuracyscatterplotannotations}[1]{For each plot, the
    root-mean-square error (RMSE) and the proportion of estimates for which the
    95\% credible interval contained the true value---$p(#1 \in
    \textrm{CI})$---is given.
}
\newcommand{\neventsplotannotations}{For each plot,
    the proportion of simulation replicates for which the number of events with
    the largest posterior probability matched the true number of
    events---$p(\hat{\nevents} = \nevents)$---is shown in the upper left
    corner,
    the median posterior probability of the correct number of events across all
    simulations---$\widetilde{p(\nevents|\alldata)}$---is shown in the upper
    right corner, and
    the proportion of simulations for which the true divergence model was
    included in the 95\% credible set---$p(\nevents \in
    \textrm{CS})$---is shown in the lower right.
}
\newcommand{\neventsbarplotannotations}{For each plot, the following summary
    statistics are shown:
    the proportion of simulation replicates for which the number of events with
    the largest posterior probability matched the true number of
    events---$p(\hat{\nevents} = \nevents)$---,
    the median posterior probability of the correct number of events across all
    simulations---$\widetilde{p(\nevents|\alldata)}$---, and
    the proportion of simulations for which the true divergence model was
    included in the 95\% credible set---$p(\nevents \in
    \textrm{CS})$---.
}
\newcommand{\neventsshadingdescription}{The number of simulation replicates
    that fall within each possible cell of true versus estimated numbers of
    events is shown, and cells with more replicates are shaded darker.
}
